A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2014-07-21 paper/discussion.tex
SFR, Fitting Model, The_Bibliography
Intro, Obs. data, SFR

Q: Mpc/h ?

>>>>

\citep{lundgren14} SFR evolution from $z=1$ to $6$

\citep{bouwens14} HST Legacy

\citep{jiang11} Keck pectroscopy

``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
luminosity (right axis) densities versus redshift (5.4). The
left axis gives the SFR densities we would infer from the measured luminosity
densities, assuming the Madau et al. (1998) conversion
factor relevant for star-forming galaxies with ages of 108 yr (see also
Kennicutt 1998). The right axis gives the U V luminosities we infer
integrating the present and published LFs to a faint-end limit of −17 mag (0.03
L∗ )''BOUWENS 2014 UV LF

### 2014-07-21 paper/introduction.tex
Intro, Obs. data, SFR

@@

@@

@@

>>>>

``An important frontier in the study of very high redshift
galaxies remains the study of their stellar populations.
Galaxies within a few hundred million years of the Big
Bang are expected to be quite different from galaxies at
lower redshift, with significantly younger ages and lower
metallicities. For very young and chemically immature
systems, changes in the stellar population could include a
transition to a more top-heavy IMF (e.g., Bromm \& Lar-
son 2004), evolution in the dust composition (e.g., due to
changes in the dust production mechanism: Maiolino et
al. 2004), as well as a much lower dust extinction overall
(e.g., Bouwens et al. 2009; Finlator et al. 2011; Dayal \&
Ferrara 2012).'' BOWENS 2014 BETA SLOPE

@@

This paper is organized as follows: In section 2... in section 3...

@@

``One of the most fundamental properties of galaxy sub-
populations at any epoch is their number density. However,
observational estimates of galaxy number densities in finite
volumes are subject to uncertainty due to cosmic variance,
arising from underlying large-scale density fluctuations and
leading to uncertainties in excess of naïve Poisson errors.
Note that this source of uncertainty is referred to as ‘sample
variance’ in other branches of cosmology. For sampling vol-
umes much larger than the typical clustering scale of the ob-
served objects, cosmic variance is not significant.''A COSMIC VARIANCE COOKBOOK

``However many important existing surveys have a sampling volume that
is small enough that cosmic variance may dominate the un-
certainties. This may be particularly true at high redshift,
where galaxies are expected to be much more strongly clus-
tered than dark matter (Kauffmann et al. 1999; Baugh et al.
1999; Coil et al. 2004; Moster et al. 2009). Still, many pub-
lished quantities which are based on number density (e.g. lu-
minosity functions, stellar mass functions, etc.) are quoted
with error budgets that do not properly account for cosmic
variance. As shown by Trenti \& Stiavelli (2008), the normal-
ization and the slope of high-redshift luminosity functions can
be affected by cosmic variance errors.''A COSMIC VARIANCE COOKBOOK

``Somerville et al. (2004) provided predictions that could be
used to estimate cosmic variance as a function of mean red-
shift and survey volume, using the number density of the pop-
ulation to estimate the bias, assuming one galaxy per halo.'' A COSMIC VARIANCE
COOKBOOK

===========>>>>>>>>> COSMIC VARIANCE CALCULATOR <<<<<<<<<===============
Results obtained using CosmicVarianceCalculator v1.02 
Developed by Michele Trenti \& Massimo Stiavelli 
If you use these results in scientific papers, please refer to:  
Trenti \& Stiavelli (2008), ApJ, 676, 767

@@

READ THIS PAPER
Vale - Ostriker
arXiv:astro-ph/0402500v2 6 Jul 2004
Mon. Not. R. Astron. Soc.
Linking halo mass to galaxy luminosity

``In recent years, N-body numerical simulations have given us
a good understanding of dark matter structure for standard
cosmological scenarios, while large scale observational
surveys have done the same for the distribution of galaxies'' arXiv:0402500v2

``More indirect approaches have also been studied.
The halo occupation distribution (HOD) model (Seljak
2000; Benson 2001; Bullock, Wechsler, \& Somerville 2002;
Zheng et al. 2002; Berlind \& Weinberg 2002; Berlind et al.
2003; Magliocchetti \& Porciani 2003) is based on the prob-
ability P(N|M) that a halo of mass M is host to N galax-
ies. By specifying the P(N|M) function, along with some
form for the distribution of dark matter and galaxies within
each halo, it is then possible to relate different statistical
indicators of the dark matter and galaxy distributions, such
as correlation functions, to each other. This fully specifies
the bias between the galaxy and the underlying matter dis-
tributions. '' arXiv:0402500v2

``Other authors have used a slightly different method.
Instead of trying to specify the number of galaxies in each
halo, they treat the halo as a whole and identify it with
a galaxy group. Then, by comparing the group luminosity
function with the halo mass function, they obtain the lu-
minosity associated with each halo (Peacock \& Smith 2000;
Marinoni \& Hudson 2002), '' arXiv:0402500v2

============>>>>>>>>> Check Peacock \& Smith 2000; Marioni \& Hudson 202

### 2014-07-21 paper/star_formation_rate.tex
Intro, Obs. data, SFR

Kennicutt pruposed a method in wich a linear relation between SFR and
luminosity in specific wavelength ranges can be assumed. This model allows to
estimate the young stars fraction and the mean SFR over periods of $10^8 - 10^9
\textrm{yr}$. The luminosity in the model, comes from the UV and the FIR
broadband, also from speciffic recombination lines.

In a typical galaxy spectrum the visible wavelengths are dominated by the main 
sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
a significative contribution from the young stars rather than the old stars. 
The infrared and far infrared wavelengths emission is dominated by dust, this 
dust is  heated by the whole stellar popullation, in particular by young, 
UV-bright stars \citep{law11}.The UV broadband emission is dominated by blue 
stars with temperature near to 40.000K. These hot and massive stars has a 
lifetime of $10^8\textrm{Gyr}$, they spend their nuclear fuel faster than smaller 
and cooler sunlike stars.

The relation between UV luminosity and Star Formation Rate \citep{kennicutt98} 
is given by:
  $ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
\right)$
  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
 and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

@@

The UV dust absorption \citep{kennicutt09} is not taken account in this work.

DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---

>>>>

There is a  method\citep{madau98} in wich a linear relation between SFR
and luminosity in specific wavelength ranges can be assumed. This model allows
to estimate the young stars fraction and the mean SFR over periods of $10^8 -
10^9 \textrm{yr}$\citep{kennicutt98}. The luminosity in the model, comes from
the UV and the FIR broadband, also from speciffic recombination lines.

%``The UV continuum emission from a galaxy with significant ongoing star
%formation is entirely dominated by late-O/early-B stars on the main sequence.
%As these have masses $>10 M_\odot$ and lifetimes $t_{ms} 2\times 10^7 yr$, the
%measured luminosity becomes proportional to the stellar birthrate and
%independent of the galaxy history for $t\gg t_{ms}$ .'' MADAU 1998
%\citep{madau98}

In a typical galaxy spectrum the visible wavelengths are dominated by the main 
sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
a significative contribution from the young stars rather than the old stars. 
The infrared and far infrared wavelengths emission is dominated by dust, this 
dust is  heated by the whole stellar popullation, in particular by young, 
UV-bright stars \citep{law11}.

On active galaxies the UV broadband emission is dominated by late-O
and early-B type stars, with temperature near to 40.000K. These hot and massive
stars has a lifetime below $10^7\textrm{Gyr}$, they spend their nuclear fuel
faster than smaller and cooler sunlike stars.

The relation between UV luminosity and Star Formation Rate
\citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
 and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

@@

The UV dust absorption \citep{kennicutt09} is not taken account in this work.
%DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---
